\documentclass[a4paper,12pt]{article}

\usepackage{geometry}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{graphicx}

\geometry{margin=1in}

\title{\textbf{1-1 TCP File Transfer System}}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Introduction}


This report is about the design, implementation and organization of the 1-1 File transfer over TCP system. The system consists of 2 components: server and client. The client connects and sends a text file to the server, the server reads and saves the content inside that file.

\section*{Protocol Design}
The protocol involves the following steps:
\begin{enumerate}

    \item The server listens for incoming connections.
    \item The client establishes a TCP connection with the server.
    \item The client reads a file and sends data to the server.
    \item The server receives the file content and saves it locally.
    \item Both client and server close the connection.
\end{enumerate}

\subsection*{Protocol Flow}
The communication protocol flow is represented below:
\begin{verbatim}
+----------+               +----------+
|  Client  |               |  Server  |
+----------+               +----------+
     |                           |
     |   Connect                 |
     |-------------------------->|
     |                           |
     |   Send file data          |
     |-------------------------->|
     |                           |
     |   Close connection        |
     |-------------------------->|
     |                           |
+----------+               +----------+
|  Close   |               |  Close   |
+----------+               +----------+
\end{verbatim}

\section*{System Organization}
The system is organized into two main components:
\begin{enumerate}
    \item \textbf{Client:} Reads a file and transmitting its content to the server.
    \item \textbf{Server:} Listens for incoming connections, receives file data, and saves it to a local file.
\end{enumerate}

\subsection*{System Architecture}
The architecture is shown below:
\begin{verbatim}
+--------------------+      +--------------------+
| Client             |      | Server             |
|--------------------|      |--------------------|
| Socket Interface   |      | Socket Interface   |
| File Reader        |      | File Writer        |
+--------------------+      +--------------------+
\end{verbatim}

\section*{Implementation}


\subsection*{Client Code Snippet}
\begin{lstlisting}[language=python]
try:
            with open(filename, "r") as fi:
                data = fi.read()
                while data:
                    sock.send(data.encode())
                    data = fi.read()
            
            print("File data sent successfully.")

        except FileNotFoundError:
            print('File not found!')

\end{lstlisting}

\subsection*{Server Code Snippet}
\begin{lstlisting}[language=python]
if data:
           
            filename = 'recv.txt'
            with open(filename, "w") as fo:
                while data:
                    fo.write(data)
                    data = conn.recv(1024).decode()
            
            print("Data written in the file successfully.")

\end{lstlisting}

\section*{Responsibilities}
\begin{enumerate}
    \item \textbf{Client:}
    \begin{itemize}
        \item Establishes a TCP connection to the server.
        \item Reads the file and sends its content.
    \end{itemize}
    \item \textbf{Server:}
    \begin{itemize}
        \item Accepts incoming connections.
        \item Receives file content and saves it locally.
    \end{itemize}
\end{enumerate}

\end{document}
